### 2008-12-21 talk/ecoop2009/intro.tex
first submission

\section{Introduction}

Dynamic languages are increasingly popular etc. etc.

The easiest way to implement a dynamic language such as Python is to write an
interpreter; however, interpreters are slow.

@@

PyPy's approach \cite{RiBo07_223} is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

Instead of emitting code for a real CPU, the generated JIT compilers described
in this paper emit code for a virtual machine: before being executed, the
emitted code will be compiled again by .NET's own JIT compiler, thus having
two \emph{layers} of JIT compilation.

>>>>

\section{Introduction}
The easiest way to implement a dynamic language such as Python is to write an
interpreter; however, interpreters are slow.

@@

PyPy's approach \cite{RiBo07_223} is to automatize the generation of JIT compilers in order
to minimize the effort required to get a fast implementation of a
dynamic language; automatic generation of JIT compilers is done with
the help of partial evaluation techniques and requires the user only
to provide an interpreter with some manual annotations which hint
the generator how interpretation and JIT compilation has to be interleaved.

More precisely, in this paper we focus on the ability of generating a JIT compiler able to emit code
for the .NET virtual machine. To our knowledge, this is the first experiment with an interpreter with
two \emph{layers} of JIT compilation, since, before being executed, the
emitted code is eventually compiled again by .NET's own JIT compiler.
